---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sigstash

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/sigstash)](https://CRAN.R-project.org/package=sigstash)
[![R-CMD-check](https://github.com/selkamand/sigstash/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/sigstash/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

**sigstash** makes it easy to load common mutational signature collections into R.

To visualise or simulate decompositions using these signatures, check out the [**sigverse**](https://github.com/selkamand/sigverse)



## Installation

You can install the development version of sigstash from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("selkamand/sigstash")
```

## Quick Start

There are only 3 commands you need to know.

1. `sig_available` will list available signature collections

2. `sig_load('collection_name')` will load the signature collection

3. `sig_load_annotations('collection_name')` will load signature-level annotations (e.g. associated aetiologies) 


### List available datasets

```{r}
library(sigstash)

sig_available()
```

### Load and Visualise datasets

```{r}
cosmic_signatures = sig_load('COSMIC_v3.3.1_SBS_GRCh38')
```


### Load signature metadata

Some signature collections will include signature level annotations for example describing aetiologies typically associated with signatures. These can be loaded using `sig_load_annotations`

```{r}
sig_load_annotations('COSMIC_v3.3.1_SBS_GRCh38')
```


